---
title: "Data Science CAP - week 2 - EDA"
author: "P.Z"
date: "2/21/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download and unzip data set

The following lines of code are aimed to download and unzip the data set:

```{r}
temp <- tempfile()
download.file("https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip",temp)
data <- read.table(unz(temp, "Coursera-SwiftKey.zip"))
unlink(temp)
```

## Load Packages
The following lines of code will load the needed packages for processing the text files and performing exploratory data analysis.

```{r}
library(stringi)
library(NLP)
library(tm)
library(RWeka)
library(ggplot2)
library(ggwordcloud)
library(patchwork)
```

## Load data

There are several data sets in the downloaded zip file but we will only focus on English language files: en_US.blogs.txt, en_US.news.txt, en_US.twitter.txt

```{r}
dtblog <- readLines("final/en_US/en_US.blogs.txt", warn = FALSE, encoding = "UTF-8")
dtnews <- readLines("final/en_US/en_US.news.txt", warn = FALSE, encoding = "UTF-8")
dttwitter <- readLines("final/en_US/en_US.twitter.txt", warn = FALSE, encoding = "UTF-8")
```

## High-level summaries

Lets check the basic summaries of the 3 data sets: file size, number of lines, total number of words, minimum/maximum/mean number of words per line.
```{r}
files = list(dtblog, dtnews, dttwitter)
filesize <- sapply(files, function(x){format(object.size(x), "MB")})
lines <- sapply(files, function(x){length(x)})
words_per_line <- sapply(files, function(x){stri_count_words(x)})
total_words <- sapply(words_per_line, function(x){sum(x)})
min_words <- sapply(words_per_line, function(x){min(x)})
max_words <- sapply(words_per_line, function(x){max(x)})
mean_words <- sapply(words_per_line, function(x){mean(x)})
file_summary <- data.frame(
  Type = c("blog", "news", "twitter"), 
  FileSize = filesize, 
  Line = lines, 
  Words = total_words, 
  Min_Words = min_words, 
  Max_Words = max_words, 
  Mean_Words = mean_words
)
file_summary
```

```{r}
```
